ThesisStuff

### 2018-05-14 ElliesThesisFigs.Rmd
Trying to adjust and log our data to make it similar to LogR values from arrays.

rp = ggplot(endos.r, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,110) +
  facet_grid(~Status) +
  geom_bar(stat='identity', show.legend = F) + 
  geom_errorbar(color='grey21', width=0.2, alpha=0.5) +
  geom_text(aes(y=pred.r*100+2, label=paste(round(pred.r*100), '%', sep='')), color='black') +
  geom_text(aes(y=10, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='High risk predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  theme( axis.text.x=element_text(angle=45,hjust=1) ) 
rp
ggsave(filename='thesis/pred_endo.png', plot=rp, width=11, height=5, units='in', dpi=300, scale=1)

@@

>>>>

rp = ggplot(endos.r, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,110) +
  facet_grid(~Status) +
  geom_bar(stat='identity', show.legend = F, fill=riskCols[2]) + 
  geom_errorbar(color='grey21', width=0.2, alpha=0.5) +
  geom_text(aes(y=pred.r*100+2, label=paste(round(pred.r*100), '%', sep='')), color='black') +
  geom_text(aes(y=5, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='High risk predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  theme( axis.text.x=element_text(angle=45,hjust=1) ) 
rp
ggsave(filename='thesis/pred_endo.png', plot=rp, width=11, height=8, units='in', dpi=300, scale=1)

@@

repeats$Probability = round(repeats$Probability, 2)

write.table(repeats, sep='\t', quote=F, row.names=F, file='tech_repeats.txt')
